HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
edited

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{\S\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
%\newcommand{\oa}[1]{}
\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
%\newcommand{\bh}[1]{}

@@

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by giving
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate}.
However, while providing the gold standard for MT evaluation, human evaluation
is not a scalable solution.
%and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

@@

\begin{table}[t]
\begin{center}
{\small
\begin{tabular}{l|cccc}
& cs & de & pl & ro \\
\hline
Annot. 1 & 255 & 140  & 138 & 96 \\
Annot. 2 & -- & 162 & 229 & 207 \\
\end{tabular}
\caption{Median annotation times per sentence, in seconds.
  In the case of the second Czech 
  ``annotator'', no timing information is available, as
  this was a collection of annotators, working in parallel.}
\label{tab:annot_times}
}
\end{center}
\end{table}

@@

}
\end{tabular}
\caption{Confusion matrices for each of the language pairs, plotted as heatmaps.}
\label{fig:heatmap}
\end{figure}

@@

Looking more closely at the areas of disagreement, we see that for the Polish structural units, the 
proportion of As was quite different between the two annotators (53\% vs. 71\%), whereas for other
languages the annotators agree in the proportions. We believe that this was because one of the Polish
annotators did not fully understand the guidelines for structural units, and percolated
errors up the tree, creating more Bs. For the German lexical units, and Czech structural units, where
Kappa is also around 0.3, the proportion of such units being marked as ``correct'' is relatively 
high, meaning that the class distribution is more skewed, so the expected agreement used in the
Kappa calculation is high, lowering Kappa. Essentially, the annotation problem is harder when the classes
are more skewed. Finally we note some evidence of domain-specific disagreements, for instance the German
MT system normally translated ``review'' (as in ``systematic review'' -- a frequent term in the 
Cochrane texts) as ``\"uberpr\"ufung'', which 
one annotator marked correct, and the other (a Cochrane employee) as incorrect.

\subsection{Comparison with Crowdsourced Adequacy Judgements}\label{sec:adequacy}

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{HUME vs DA scores. DA score have been standardised for each crowdsourcing annotator and averaged across exactly 10 annotators. HUME scores are averaged where there were two annotations. 
%The regression is calculated using linear least squares.
}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{graham2015accurate,graham2015crowd,graham2015improving} has proposed a new approach for collecting 
accuracy ratings, direct assessment (DA). By crowdsourcing a large number of adequacy judgements for each candidate 
translation on a fine-grained 
scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores. 
It has been shown that mean DA judgements correlate very strongly with each other. 
We followed~\parcite{graham2015accurate} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romanian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results.

We can see in Figure~\ref{fig:dacorrelation} that HUME and Direct Assesment scores correlate reasonably well.  
The Pearsons correlation for en-de is 0.58 and for en-ro is 0.70 overall which confirms that 
the HUME metric is consistent with an accepted human evaluation method, namely DA, 
even though the two metrics are very different in their conception. 
Although DA is a valuable tool for translation research, HUME has two advantages:
it returns fine-grained semantic information about the quality of translations and it only requires one 
annotator. Direct assesment returns a single score, and it needs a large 
crowd which may not be available or reliable.

\begin{figure}[t]
\includegraphics[width=0.45\textwidth]{humevsDAcorrtypes-10en-dero.pdf}
\caption{Pearsons correlation HUME scores vs DA for different node types. Struct refers to all structural nodes, P+S are all process and state nodes, H parallel scene nodes, A participant, C centre, E elaborators, and L linker nodes.}
\label{fig:dacorrelationtypes}
\end{figure}

In Figure~\ref{fig:dacorrelationtypes} we can see an analysis of HUME correlations with DA by HUME node type. We can see that correlation increases when combining different sematic node types and that correlation is highest for node type ``all''. Some types of nodes seem to predict the DA scores better than others. The HUME scores on parallel scene nodes (H) and participant nodes (A) seem to correlate more strongly with DA than scores on process and state nodes (P+S) or linker nodes (L). Center nodes (C) are also more correlated than elaborator nodes (E), which is what we would expect given that center nodes are by definition more important to the semantics of a sentence than elaborators. We leave it to future work to construct a HUME score which weights the different node types according to their semantic relevance.

@@

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small a coronary angioplasty may not be technically possible \\
Transl.& \small eine koronare Angioplastie kann nicht technisch m{\"o}glich \\
Gloss & \small a coronary angioplasty can not technically possible \\
\end{tabular}
\end{center}

>>>>

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{\S\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
%\newcommand{\bh}[1]{}

@@

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by assigning
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate}.
However, while providing the gold standard for MT evaluation, human evaluation
is not a scalable solution.
%and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

@@

\begin{table}[t]
\begin{center}
{\small
\begin{tabular}{l|cccc}
& cs & de & pl & ro \\
\hline
Annot. 1 & 255 & 140  & 138 & 96 \\
Annot. 2 & $^*$ & 162 & 229 & 207 \\
\end{tabular}
\caption{Median annotation times per sentence, in seconds.
  $^*$: no timing information is available, as
  this was a collection of annotators, working in parallel.}
\label{tab:annot_times}
}
\end{center}
\end{table}

@@

}
\end{tabular}
\caption{Confusion matrices for each language pair.}
\label{fig:heatmap}
\end{figure}

@@

Looking more closely at the areas of disagreement, we see that for the Polish structural units, the 
proportion of As was quite different between the two annotators (53\% vs. 71\%), whereas for other
languages the annotators agree in the proportions. We believe that this was because one of the Polish
annotators did not fully understand the guidelines for structural units, and percolated
errors up the tree, creating more Bs. For German atomic and Czech structural units, where Kappa is also around 0.3, the proportion of such units being marked as ``correct'' is relatively 
high, meaning that the class distribution is more skewed, so the expected agreement used in the
Kappa calculation is high, lowering Kappa.
%ssentially, the annotation problem is harder when the classes are more skewed.
Finally we note some evidence of domain-specific disagreements, for instance
the German MT system normally translated ``review'' (as in ``systematic review'' -- a frequent term in the 
Cochrane texts) as ``\"uberpr\"ufung'', which 
one annotator marked correct, and the other (a Cochrane employee) as incorrect.

\subsection{Comparison with Direct Assessment}\label{sec:adequacy}

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{HUME vs DA scores. DA score have been standardised for each crowdsourcing annotator and averaged across exactly 10 annotators. HUME scores are averaged where there were two annotations. 
%The regression is calculated using linear least squares.
}
\label{fig:dacorrelation}
\end{figure}

Recent research~\cite{graham2015accurate,graham2015crowd,graham2015improving} has proposed a new approach for collecting accuracy ratings, direct assessment (DA). By crowdsourcing a large number of adequacy judgements for each candidate translation on a fine-grained scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores, that correlate very strongly with one other.

We followed~\parcite{graham2015accurate} and collected 10 adequacy
judgements on most of the HUME annotated translations for
German and Romanian, using the CrowdFlower platform\footnote{\url{https://www.crowdflower.com}}. To ensure high quality judgments we restricted the IP of the annotators to those of the relevant country. Czech and Polish judgements were
excluded, as our experiments only yielded very little high quality data.

Figure~\ref{fig:dacorrelation} plots the HUME score for each sentence against its DA score. HUME and Direct Assesment scores correlate reasonably well. The Pearson correlation for en-ro (en-de) is 0.70 (0.58), and 0.78 (0.74) where only doubly HUME-annotated points are taken. This confirms that HUME is consistent with an accepted human evaluation method, despite the differences in
their conception.
While DA is a valuable tool for MT research, HUME has two advantages:
it returns fine-grained semantic information about 
the quality of translations and it only requires very few annotators.
Direct assesment returns a single opaque score, and (as also noted by
Graham et al.), requires a large crowd which may not be available or reliable.

\begin{figure}[t]
\includegraphics[width=0.45\textwidth]{humevsDAcorrtypes-10en-dero.pdf}
\caption{Pearson correlation HUME scores vs DA for different node types. Struct refers to all structural nodes, P+S are all process and state nodes, H parallel scene nodes, A participant, C centre, E elaborators, and L linker nodes.}
\label{fig:dacorrelationtypes}
\end{figure}

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME correlations with DA by HUME node type. We can see that correlation is highest where all sub-sets are taken into consideration (``all'' bar), supporting our claim for the value of taking into account a rich set of semantic phenomena. Some types of nodes seem to predict the DA scores better than others. The HUME scores on Parallel Scenes (H) and Participants (A) seem to correlate more strongly with DA than scores on Scene Main Relations (P+S) or linker nodes (L). Center nodes (C) are also more correlated than elaborator nodes (E), which is what we would expect given that center nodes are by definition more important to the semantics of a sentence than elaborators. We leave it to future work to construct a HUME score which weights the different node types according to their semantic relevance.\oa{I think we should be careful here. It may very well be that these stem from the number of nodes taken into account. I think we should also say explicitly that .}
This is also a demonstration of the more refined analysis (allowing to slice the data by semantic phenomena) enabled by taking a semantic approach to MT evaluation.

@@

\vspace{-.3em}
\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small a coronary angioplasty may not be technically possible \\
Transl.& \small eine koronare Angioplastie kann nicht technisch m{\"o}glich \\
Gloss & \small a coronary angioplasty can not technically possible \\
\end{tabular}
\end{center}
\vspace{-.5em}
